Interactively Visualizing Clustering in Multivariate Data Using pytourr

### 2024-09-06 manuscript.tex
small changes

%% almost as usual
\author{Matthias Medl\,\orcidlink{0000-0002-3354-4579}\\ Institute of Statistics \\ BOKU University \\ Vienna \And 
        Dianne Cook\,\orcidlink{0000-0002-3813-7155}\\ Monash Data Futures Institute \\ Monash University \\ Melbourne \And
        Ursula Laa\,\orcidlink{0000-0002-0249-6439}\\ Institute of Statistics \\ BOKU University \\ Vienna}
%% \AND can be used instead of \And and starts a new line
\title{pytourr: Interactive Visualization Interface for the tourr Package}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Matthias Medl, Dianne Cook, Ursula Laa} %% comma-separated
\Plaintitle{pytourr: Interactive Visualization Interface for the tourr Package} %% without formatting
\Shorttitle{pytourr} %% a short title (if necessary)

@@

\section{Similar work}

@@

\section{Datasets}

Two datasets were analysed as part of this study. The Austrian Vacation Activities \cite{dolnicar2003winter} dataset and the the Australian Vacation Activities \cite{cliff2009formative} dataset.

>>>>

%% almost as usual
\author{Matthias Medl\,\orcidlink{0000-0002-3354-4579}\\ Institute of Statistics \\ BOKU University \\ Vienna \And 
        Dianne Cook\,\orcidlink{0000-0002-3813-7155}\\ Econometrics and Business Statistics \\ Monash University \\ Melbourne \And
        Ursula Laa\,\orcidlink{0000-0002-0249-6439}\\ Institute of Statistics \\ BOKU University \\ Vienna}
%% \AND can be used instead of \And and starts a new line
\title{Interactively Visualizing Clustering in Multivariate Data Using pytourr}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Matthias Medl, Dianne Cook, Ursula Laa} %% comma-separated
\Plaintitle{Interactively Visualizing Clustering in Multivariate Data Using pytourr} %% without formatting
\Shorttitle{pytourr} %% a short title (if necessary)

@@

\begin{itemize} \itemsep 0in
\item Background to clustering analysis
\item Visualising clusters, including tours
\item Difference between clustering and partitioning
\item How do you know whether the results are useful
\end{itemize}

\section{Related Work}

@@

\section{Applications}

The Austrian Vacation Activities \cite{dolnicar2003winter} and the Australian Vacation Activities \cite{cliff2009formative} datasets are used to illustrate the methods.
